The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/methods.tex
mentioned collision and fixed typo
smalledits

\begin{equation}
    \begin{split}
        \tr_i  & = \sum_{\prt_k \in \bar{\refX}_j} \underbrace{\mathbbm{1}^T\wt_k \samp{\Jnurbs}_k}_{B_{ik}}\vc{q}_k \\
        \vc{c}_i^1 & = \smash{\underbrace{\left(\samp{\Pmat^1}^T\wt_i\samp{\Pmat^1}\right)}_{A^1_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^1}^T\wt_i\samp{\Jnurbs}_i}_{B^1_i}\vc{q}_i-\underbrace{\samp{\Pmat^1}^T\wt_i\mathbbm{1}}_{T^1_i}\tr_i\bigg)\\
        \vc{c}_i^2 & = \smash{\underbrace{\left(\samp{\Pmat^2}^T\wt_i\samp{\Pmat^2}\right)}_{A^2_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Jnurbs}_i}_{B^2_i}\vc{q}_i-\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Pmat^1}}_{D^2_i}\vc{c}_i^1 - \underbrace{\samp{\Pmat^2}^T\wt_i\mathbbm{1}}_{T^2_i}\tr_i\bigg)
    \end{split},
    \label{eq:hfit} 
\end{equation} where $\Pmat^l$ contains only the monomial basis of order $l$,  $\samp{\Pmat^l}$ is the stacked evaluation of this matrix at the $s$ quadrature points and $\vc{c}^l_i$ are the corresponding coefficients. 
Finally, $\wt_i$ is the diagonal integration weight matrix and $\mathbbm{1}\in\real^{3s\times3}$ is a matrix of stacked $3\times3$ identity matrices -- one for each quadrature point.

@@

\begin{equation}
\begin{aligned}
\mathbf{w}(\mathbf{X}_j) =  \arg\min_{\mathbf{w}} \quad & \mathbf{w}^T \Theta(\mathbf{X}_j) \mathbf{w}    \\
\textrm{st} \quad & 0 \leq w_i \leq 1 \mbox{ }\forall i                    \\
                  &   \sum_i^n w_i = 1                      \\
\end{aligned}
\end{equation}

@@

This post-process ensures that our blending weights partition unity and are non-negative~(\reffig{distance_weight_puft}). 
For any point on a part that is non-intersecting, the weights will satisfy the Kronecker delta property since the inverse distance weights imply that only
a single $\Theta_i$ will have a non-infinite weight. 
For points that lie on more than one part, the weights associated with the intersecting parts will be equal and all others will be zero
This implies that the deformed positions of these intersecting points will be an average, which is a plausible solution and ensures continuity.
Finally, the distance cutoff $\alpha$ allows us to control the sparsity of the blending weights. We employ a simple heuristic to select $\alpha$ by searching for a $\alpha$ that produces a set of blending weights meeting a desired sparsity target $T \in \left( 0,1\right)$, which is defined as the ratio of non-zeros to total number of weights. This yields a unitless, easy to tune parameter.

@@

Given a quadrature point group, and an edge from the associated deformation origin to $\prt_i$, we set the edge cost to be the sum, 
over all quadrature points in the group of the blending weights associated with $\prt_i$.
This cost penalizes heavily ``connected'' origin candidates, encouraging sparsity during origin selection. 
This amounts to minimizing the following integer linear program:
\begin{equation}
\begin{aligned}
\mathbf{f} =  \arg\min_{\mathbf{f}} \quad & \mathbf{c}^T \mathbf{f}    \\
\textrm{st} \quad & A_{\text{cons}} \mathbf{f} = 0  \\
                  & f_i \in \integer \mbox{ }\forall i	\\
                  & 0 \leq f_i \leq u_i
\end{aligned}
\end{equation}
where $\mathbf{f}$ and $\mathbf{c}$ are the edge flow and cost values, respectively, assembled into vectors, and $A_{\text{cons}}$ forms the set of constraints satisfying the flow conservation constraint. 
We solve this using the dual simplex solver in MATLAB.
%\ty{we use the default in intlinprog, which should be dual-simplex} We choose $\XBs$ to be all the deformation origin candidates in $A$ that have an outgoing flow of at least $1$.

>>>>

\begin{equation}
    \begin{split}
\tr_i  & = \frac{1}{\sum_{\prt_k \in \bar{\refX}_j} \Tr \wt_k}
        \sum_{\prt_k \in \bar{\refX}_j} \underbrace{\mathbbm{1}^T\wt_k \samp{\Jnurbs}_k}_{B_{ik}}\vc{q}_k \\   
        \vc{c}_i^1 & = \smash{\underbrace{\left(\samp{\Pmat^1}^T\wt_i\samp{\Pmat^1}\right)}_{A^1_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^1}^T\wt_i\samp{\Jnurbs}_i}_{B^1_i}\vc{q}_i-\underbrace{\samp{\Pmat^1}^T\wt_i\mathbbm{1}}_{T^1_i}\tr_i\bigg)\\
        \vc{c}_i^2 & = \smash{\underbrace{\left(\samp{\Pmat^2}^T\wt_i\samp{\Pmat^2}\right)}_{A^2_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Jnurbs}_i}_{B^2_i}\vc{q}_i-\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Pmat^1}}_{D^2_i}\vc{c}_i^1 - \underbrace{\samp{\Pmat^2}^T\wt_i\mathbbm{1}}_{T^2_i}\tr_i\bigg)
    \end{split},
    \label{eq:hfit} 
\end{equation} where $\Pmat^l$ contains only the monomial basis of order $l$,  $\samp{\Pmat^l}$ is the stacked evaluation of this matrix at the $s$ quadrature points and $\vc{c}^l_i$ are the corresponding coefficients. 
Finally, $\wt_i$ is the diagonal integration weight matrix and $\mathbbm{1}\in\real^{3s\times3}$ is a matrix of stacked $3\times3$ identity matrices -- one for each quadrature point.

@@

\begin{equation}
\begin{aligned}
\mathbf{w}(\mathbf{X}_j) =  \arg\min_{\mathbf{w}} \quad & \mathbf{w}^T \Theta(\mathbf{X}_j) \mathbf{w}    \\
\textrm{s.t.} \quad & 0 \leq w_i \leq 1 \mbox{ }\forall i                    \\
                  &   \sum_i^n w_i = 1                      \\
\end{aligned}
\end{equation}

@@

This post-process ensures that our blending weights partition unity and are non-negative~(\reffig{distance_weight_puft}). 
For any point on a part that is non-intersecting, the weights will satisfy the Kronecker delta property since the inverse distance weights imply that only
a single $\Theta_i$ will have a non-infinite weight. 
For points that lie on more than one part, the weights associated with the intersecting parts will be equal and all others will be zero
This implies that the deformed positions of these intersecting points will be an average, which is a plausible solution and ensures continuity.
Finally, the distance cutoff $\alpha$ allows us to control the sparsity of the blending weights. We employ a simple heuristic to select $\alpha$ by searching for one that produces a set of blending weights meeting a desired sparsity target $T \in \left( 0,1\right)$, which is defined as the ratio of non-zeros to total number of weights. This yields a unitless, easy to tune parameter.

@@

Given a quadrature point group, and an edge from the associated deformation origin to $\prt_i$, we set the edge cost to be the sum, 
over all quadrature points in the group of the blending weights associated with $\prt_i$.
This cost penalizes heavily ``connected'' origin candidates, encouraging sparsity during origin selection. 
This amounts to minimizing the following integer linear program:
\begin{equation}
\begin{aligned}
\mathbf{f} =  \arg\min_{\mathbf{f}} \quad & \mathbf{c}^T \mathbf{f}    \\
\textrm{s.t.} \quad & A_{\text{cons}} \mathbf{f} = 0  \\
                  & f_i \in \integer \mbox{ }, \forall i	\\
                  & 0 \leq f_i \leq u_i
\end{aligned}
\end{equation}
where $\mathbf{f}$ and $\mathbf{c}$ are the edge flow and cost values, respectively, assembled into vectors, and $A_{\text{cons}}$ forms the set of constraints satisfying the flow conservation constraint. 
We solve this using the dual simplex solver in MATLAB.
%\ty{we use the default in intlinprog, which should be dual-simplex} We choose $\XBs$ to be all the deformation origin candidates in $A$ that have an outgoing flow of at least $1$.
